An Analysis of the Feasibility and Performance of BitTorrent as a Data Transfer Protocol in Peer to Peer Backup Systems

### 2014-04-30 paper/paper.tex
Paper: Fix citations.

\bibitem{dropboxusers} https://www.dropbox.com/news/company-info
\bibitem{oneddriveusers} http://blog.onedrive.com/over-250m-people-using-skydrive/
\bibitem{ChurnResilient} S. Legtchenko, S. Monnet, P. Sens, G. Muller, Churn-Resilient Replication Strategy for Peer-to-Peer Distributed Hash-Tables
\bibitem{Kademlia} P. Maymounkov, D. Mazi\`eres, Kademlia: A Peer-to-Peer Information System Based on the XOR Metric
\bibitem{pStore} C. Batten, K. Barr, A. Saraf, S. Trepetin, pStore: A Secure Peer-to-Peer Backup System
\bibitem{PeerStore} M. Landers, H. Zhang, K. Tan, PeerStore: Better Performance by Relaxing in Peer-to-Peer Backup
\bibitem{StorageSearchP2PNetworks} J. Augustine, A. Molla, E. Morsy, G. Pandurangan, Storage and Search in Dynamic Peer-to-Peer Networks
\bibitem{p2pSurvey} A. Passarella, A survey on content-centric technologies for the current Internet: CDN and P2P solutions
\bibitem{BTSyncFAQ} http://www.bittorrent.com/help/faq/sync
\bibitem{btsynctech} http://www.bittorrent.com/sync/technology
\bibitem{btsyncuserguide} http://btsync.s3-website-us-east-1.amazonaws.com/BitTorrentSyncUserGuide.pdf
\bibitem{btsyncapi} http://www.bittorrent.com/sync/developers/api
\bibitem{cryptoDef} Rivest, Ronald L. (1990). "Cryptology". In J. Van Leeuwen. Handbook of Theoretical Computer Science 1. Elsevier.
\bibitem{bittorrentDHT} http://www.bittorrent.org/beps/bep\_0005.html
\bibitem{bittorrentProtocol} http://www.bittorrent.org/beps/bep\_0003.html
\bibitem{syslogRFC1} C. Lonvick, "The BSD syslog Protocol". https://tools.ietf.org/html/rfc3164, August 2001.
\bibitem{syslogRFC2} R. Gerhards, "The syslog Protocol". https://tools.ietf.org/html/rfc5424, March 2009.
\bibitem{skypeSupernode} S. Guha, N. Daswani, R. Jain, "An Experimental Study of the Skype Peer-to-Peer VoIP System". http://saikat.guha.cc/pub/iptps06-skype/ .
\bibitem{kademliaDHT} P. Maymounkov, D. Mazi\`eres, Kademlia: A Peer-to-peer Information System Based on the XOR Metric, IPTPS '01 Revised Papers from the First International Workshop on Peer-to-Peer Systems (2002), 53-65.
\bibitem{internetUsersByCountry} International Telecommunications Union (Geneva), Percentage of Individuals using the Internet 2000-2012, June 2013, retrieved 29 April 2014.
\bibitem{downloadSpeedsByCountry} Ookla, Household Download Index, April 2014, accessed from http://www.netindex.com/download/allcountries/ on 29 April 2014.

>>>>

\bibitem{dropboxusers} Dropbox. "Company Info". Retrieved on 29 April 2014 from https://www.dropbox.com/news/company-info .
\bibitem{oneddriveusers} O. Shahine. "Over 250M people using SkyDrive". 6 May 2013. Retrieved on 29 April 2014 from http://blog.onedrive.com/over-250m-people-using-skydrive/ .
\bibitem{ChurnResilient} S. Legtchenko, S. Monnet, P. Sens, G. Muller. "Churn-Resilient Replication Strategy for Peer-to-Peer Distributed Hash-Tables". July 2012. ACM Transactions on Autonomous and Adaptive Systems (TAAS) Volume 7 Issue 2. Article No. 28 
\bibitem{Kademlia} P. Maymounkov, D. Mazi\`eres. "Kademlia: A Peer-to-Peer Information System Based on the XOR Metric". 2002. IPTPS '01 Revised Papers from the First International Workshop on Peer-to-Peer Systems, Pages 53-65
\bibitem{pStore} C. Batten, K. Barr, A. Saraf, S. Trepetin, "pStore: A Secure Peer-to-Peer Backup System". 2001. 
\bibitem{PeerStore} M. Landers, H. Zhang, K. Tan. "PeerStore: Better Performance by Relaxing in Peer-to-Peer Backup". 2004. P2P '04 Proceedings of the Fourth International Conference on Peer-to-Peer Computing, Pages 72-79 
\bibitem{StorageSearchP2PNetworks} J. Augustine, A. Molla, E. Morsy, G. Pandurangan. "Storage and Search in Dynamic Peer-to-Peer Networks". 2013. SPAA '13 Proceedings of the twenty-fifth annual ACM symposium on Parallelism in algorithms and architectures, Pages 53-62 
\bibitem{p2pSurvey} A. Passarella. "A survey on content-centric technologies for the current Internet: CDN and P2P solutions". January 2012. Computer Communications Volume 35 Issue 1, Pages 1-32
\bibitem{BTSyncFAQ} BitTorrent, Inc. "Frequently Asked Questions". Retrieved on 29 April 2014 from http://www.bittorrent.com/help/faq/sync .
\bibitem{btsynctech} BitTorrent, Inc. "Technology". Retrieved on 29 April 2014 from http://www.bittorrent.com/sync/technology .
\bibitem{btsyncuserguide} BitTorrent, Inc. "BitTorrent Sync User Guide". Retrieved on 29 April 2014 on http://btsync.s3-website-us-east-1.amazonaws.com/BitTorrentSyncUserGuide.pdf .
\bibitem{btsyncapi} BitTorrent, Inc. "BitTorrent Sync API Beta". Retrieved on 29 April 2014 from http://www.bittorrent.com/sync/developers/api .
\bibitem{cryptoDef} R. Rivest. "Cryptology". J. Van Leeuwen. Handbook of Theoretical Computer Science 1. Elsevier.
\bibitem{bittorrentDHT} A. Loewenstern, A. Norberg. "DHT Protocol". 31 January 2008. Retrieved on 29 April 2014 from http://www.bittorrent.org/beps/bep\_0005.html .
\bibitem{bittorrentProtocol} B. Cohen. "The BitTorrent Protocol Specification". 10 January 2008. Retrieved on 29 April 2014 from http://www.bittorrent.org/beps/bep\_0003.html .
\bibitem{syslogRFC1} C. Lonvick, "The BSD syslog Protocol". August 2001. Retrieved on 29 April 2014 from https://tools.ietf.org/html/rfc3164.
\bibitem{syslogRFC2} R. Gerhards, "The syslog Protocol". March 2009. Retrieved on 29 April 2014 from https://tools.ietf.org/html/rfc5424.
\bibitem{skypeSupernode} S. Guha, N. Daswani, R. Jain, "An Experimental Study of the Skype Peer-to-Peer VoIP System". Retrieved on 29 April 2014 from http://saikat.guha.cc/pub/iptps06-skype/ .
\bibitem{kademliaDHT} P. Maymounkov, D. Mazi\`eres. "Kademlia: A Peer-to-peer Information System Based on the XOR Metric". 2002. IPTPS '01 Revised Papers from the First International Workshop on Peer-to-Peer Systems, 53-65.
\bibitem{internetUsersByCountry} International Telecommunications Union (Geneva). "Percentage of Individuals using the Internet 2000-2012". June 2013. Retrieved on 29 April 2014 from http://www.itu.int/en/ITU-D/Statistics/Documents/statistics/2013/Individuals\_Internet\_2000-2012.xls .
\bibitem{downloadSpeedsByCountry} Ookla. "Household Download Index". April 2014. Retrieved on 29 April 2014 from http://www.netindex.com/download/allcountries/ .
